The CMS Data Aggregation System

### 2010-05-04 doc/paper.tex
Dave fixed the abstract
git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@683 4525493e-7705-40b1-a816-d608a930855b

\begin{abstract}
Meta-data plays significant role in large modern enterprises, 
research experiments and digital libraries where it comes from a different 
sources and distributed in a variety of forms and digital formats. 
It is organized and managed by constantly evolving software using 
both relational and non-relational data sources. Even though we can apply
information retrieval approach to non-relation data sources,
we can't do so for relational ones, where information is accessed via
pre-established set of data-services.

Here we discuss a new data aggregation system which consumes, 
indexes and delivers information from different relational and 
non-relational data sources to answer cross data-service queries 
and explore meta-data associated with petabytes of experimental data. 
We combine simplicity of keyword-based search with precision of RDMS
under the new system. The aggregated information being collected from various sources,
allowing end-users to place dynamic queries, get precise answers and 
trigger information retrieval on demand. Such close to real-time system 
based on studies  of use cases of the CMS particle physics experiment at 
the LHC where we used a large scale, distributed computing environment 
to motivate this work.
\end{abstract}

>>>>

\begin{abstract}
Metadata plays a significant role in large modern enterprises, 
research experiments and digital libraries where it comes from many different 
sources and is distributed in a variety of digital formats. 
It is organized and managed by constantly evolving software using 
both relational and non-relational data sources. Even though we can apply
an information retrieval approach to non-relation data sources,
we can't do so for relational ones, where information is accessed via
a pre-established set of data-services.

Here we discuss a new data aggregation system which consumes, 
indexes and delivers information from different relational and 
non-relational data sources to answer cross data-service queries 
and explore metadata associated with petabytes of experimental data. 
We combine the simplicity of keyword-based search with the precision of RDMS
under the new system. The aggregated information is collected from various sources,
allowing end-users to place dynamic queries, get precise answers and 
trigger information retrieval on demand. Based on the use cases of the CMS experiment, 
we have performed a set of detailed, large scale tests the results of which 
we present in this paper.
\end{abstract}
